<small> Supplementary materials for the main submission entitled - <br><br> Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2021-06-11 paper/paper-supplementary.Rmd
display correct till Figure 10 done

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE,
        tinytex.verbose = FALSE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
library(kableExtra)
library(distributional)
library(ggplot2)
library(sugrrants)
library(here)
library(ggplot2)
library(patchwork)
library(readr)
library(tidyverse)
library(here)
library(broom)

@@

```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,5) distribution. For each panel, it could be seen that the location shifts to the right for increasing x levels. Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE,
        tinytex.verbose = FALSE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(viridis)
library(tsibble)
library(gravitas)
library(ggpubr)
library(readr)
library(kableExtra)
library(distributional)
library(ggplot2)
library(sugrrants)
library(here)
library(ggplot2)
library(patchwork)
library(readr)
library(tidyverse)
library(here)
library(broom)
library(latex2exp)

@@

```{r nxbyfacet-ridge-N01-onegran, fig.cap="Ridge plots of raw wpd is shown for N(0,1) distribution. For each panel, it could be seen that the location shifts to the right for increasing x levels. Across each panel, the scale of the distribution seems to change for low/moderately lower values and higher values of nfacets and left tails are longer for lower facet levels."}
knitr::include_graphics(here::here("simulations/supplementary/one-gran/raw/null_design_quantrans/figs/nxbyfacet_ridge_wpd_N01.png"))
```
